\newpage
\thispagestyle{empty}

\begin{center}
\emph{\LARGE Acknowledgement}\\[2.5cm]
\end{center}

\normalsize I would like to acknowledge my indebtedness and render my warmest thanks
to my guide \textbf{prof. Nilesh Vani}, who made this work possible. His friendly guidance and expert advice have been invaluable throughout all stages of the work. I would also wish to express my gratitude to my Head of Department \textbf{Prof. Pramod Gosavi} for extended discussions and valuable suggestions which have contributed greatly to the improvement of the thesis. The thesis has also benefited from comments and suggestions made by \textbf{Prof. Rahul Gaikwad} who have read through the manuscript. I take this opportunity to thank them.My special thanks are extended to my \textbf{Principal Prof. (Dr) V. G. Arajpure}, for the drawing on the cover.

Special thanks are due to my husband, \textbf{Mr. Harish Gadade}, for his continuous support and understanding, but also for more concrete thinks like commenting on earlier versions of the thesis, helping with the figures and the final preparation of the manuscript. I want to thank my friend \textbf{Tasneem} and my sisters \textbf{Rituja} and \textbf{Snehal}, for constant encouragement. I would like to thank the Computer Department of my college for providing excellent working conditions. Also I thank all those who have supported me directly or indirectly\\[1.0cm]





% Bottom of the page
\begin{flushright}
Priyanka B. Waghmode\\
Student Computer science and Engg.\\
Godavari College of Engineering, Jalgaon(M.S.) 
\end{flushright}

